Water Management

### 2020-02-11 Paper/paper.tex
some more details on steady states
fix typo in textit

Now, it's trivial to compute the flow at any given time using code, simply by implementing the formula as given above. However, if we want to compute the amount of water flowing through the pipe in the time interval $[0.25, 0.5]$, we can not calculate that directly, as we would have to know the antiderivative of $f(t)$. Apart from this example, it's not always trivial to calculate the antiderivative of a function analytically. However it is possible compute the area below (almost) any function using numerical integration, also called numerical quadrature.

@@

which equals to finding the column $aux$ that maximizes the expected value over all states (TODO: kann man das so sagen?). We repeat this step over and over again until the our value function $V$ converges (technically: the norm of the difference between $V'$ and $V$ falls below a certain tolerance value).

Finally, we want to compute the value for the steady state.

@@

	The result is put in a histogram and shown in figure \ref{fig:steadyStateMonteCarlo}

>>>>

Now, it's trivial to compute the flow at any given time using code, simply by implementing the formula as given above. 
However, if we want to compute the amount of water flowing through the pipe in the time interval $[0.25, 0.5]$, we can not calculate that directly, as we would have to know the antiderivative of $f(t)$. 
Apart from this example, it's not always trivial to calculate the antiderivative of a function analytically. 
[TODO: zwei mal however]However it is possible compute the area below (almost) any function using numerical integration, also called numerical quadrature.

@@

which equals to finding the column $aux$ that maximizes the expected value over all states (TODO: kann man das so sagen?).
We repeat this step over and over again until the our value function $V$ converges (technically: the norm of the difference between $V'$ and $V$ falls below a certain tolerance value). \\

Finally, we want to compute the value of the steady state by using a monte carlo simulation.

@@

	The result is put in a histogram and shown in figure \ref{fig:steadyStateMonteCarlo}.
	The highest possibility for a steady state is around 4.2. 
	In edge cases one can find steady states as low as 3.5 or as high as 5.2. 
	The curve resembles a normal distribution. 
